\thesistitle

### 2019-06-05 sections/research.tex
Working on clone type definitions

\chapter{Addressing problems with clone type definitions}\label{chap:clonetypes}
For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see chapter \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can merge the clone while improving the design. Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.

@@

>>>>

\chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
In section \ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature. These simple definitions are suitable for analysis of a codebase. Their detection results in simple to understand numbers to argue about a codebase. However, these clone types have a few flaws which makes it hard to argue to what extend two fragements of code are functionally related. For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can merge the clone while improving the design. Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.

We also look into clone detection tools for their suitability to support the proposed clone type definitions. We selected a few criteria  Most clone detection tools support these definitions of clone types. However, many of these tools use a vastly different approach. A study by Saini et al \cite{saini2018towards} outlines different clone detection tools and compares their results for each of type 1-3 clones. Even though they operate on the same type definitions, the tools used in this study yield different results.

\section{Refactoring-oriented clone types}
To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored.

@@

\section{Suitability of existing Clone Detection Tools towards our refactoring purposes}
\label{ch:tool-overview}
We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze a popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones. We want to perform an analysis on all clones in projects to get a complete overview.
\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged. Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{chap:type1clones}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to allow those threshold changes. This can be either through simple changes of the source code, or by using some configuration file.
\end{enumerate}

\begin{table}[H]
 \begin{center}
  \caption{Our survey on clone detection tools.} \label{table:dettools}
  \medskip
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
\end{tabular}
\end{center}
\end{table}

None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}. This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.

\chapter{Clone Detection}

\chapter{Thresholds}
